---
title: "Lightning Network Study | Level 1 Heuristics"
author: Bernhard Haslhofer
date: "`r Sys.Date()`"
output:
  beamer_presentation:
    slide_level: 2
classoption: "aspectratio=169"
---

```{r libs_and_functions, include=FALSE}

ensure_packages <- function(packages) {
  # install of not yet done
  new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
  if(length(new.packages)) install.packages(new.packages, repos = "http://cran.us.r-project.org")
  # load libraries
  lapply(packages, library, character.only = TRUE)
}

# install (if not available) and load libraries
ensure_packages(c("tidyverse", "xtable", "assertr", "igraph", "scales"))

# set dataset path
dataset.path <- "../data/joined/level_1/"

# set results path
results.path <- "../data/joined/results/"

# set paper path
paper.path <- "~/Documents/publications/2020-LN-Analysis/"

# make sure plot path exists
dir.create(file.path("../plots"), showWarnings = FALSE)
```

## Motivation | Hypothesis

- Lighning users follow certain behavioural patterns
    - they fund several channels using the same (source) wallet
    - after closing a channel, they collect funds in the same (destination) wallet

- Each funding and settlement address can be mapped to an entity, which likely represents some user wallet (co-spent heuristics)

- Above behavioural patterns are reflected in the funding and settlement egonets and can be identified **heuristically**


```{r load_datasets, echo=FALSE, message=FALSE}

load_dataset <- function() {
  
  funding.addr_entities <- read_csv(
      paste0(dataset.path, "funding_addresses_entities.csv")
  )
  
  funding.entity_relations <- read_csv(
      paste0(dataset.path, "funding_entities_incoming_relations.csv")
  )
  
  funding.entity_stats <- read_csv(
    paste0(dataset.path, "funding_entities_stats.csv"))
  
  settlement.addr_entities <- read_csv(
      paste0(dataset.path, "settlement_addresses_entities.csv")
  )
  
  settlement.entity_relations <- read_csv(
      paste0(dataset.path, "settlement_entities_outgoing_relations.csv")
  )
  
  settlement.entity_stats <- read_csv(
    paste0(dataset.path, "settlement_entities_stats.csv"))
  
  address.categories <- read_csv(
    paste0(dataset.path, "address_categories.csv")
  )
  
  # Check dataset with assertions
  
  funding.addr_entities %>%
    assert(in_set(funding.entity_relations$funding_entity), funding_entity) %>%
    assert(in_set(funding.entity_stats$entity), funding_entity)
  
  funding.entity_relations %>%
    assert(in_set(funding.addr_entities$funding_entity), funding_entity) %>%
    assert(in_set(funding.entity_stats$entity), src_entity)
  
  settlement.addr_entities %>%
    assert(in_set(settlement.entity_stats$entity), settlement_entity)
  
  settlement.entity_relations %>%
    assert(in_set(settlement.addr_entities$settlement_entity), settlement_entity) %>%
    assert(in_set(settlement.entity_stats$entity), dst_entity)
  
  address.categories %>%
    assert(in_set(union(funding.entity_stats$repr_address, settlement.entity_stats$repr_address)), address)
  
  # Create and cache entities data frame
  
  addresses <<- bind_rows(
    funding.addr_entities %>%
      select(address = funding_address, entity = funding_entity) %>% mutate(use = 'funding'),
    settlement.addr_entities %>% 
      select(address = settlement_address, entity = settlement_entity) %>% mutate(use = 'settlement')
  ) %>%
    unique %>%
    mutate(seen = 1) %>%
    pivot_wider(names_from = use, values_from = seen)
  
  entities <<- bind_rows(
    funding.addr_entities %>% select(entity = funding_entity) %>% mutate(use = 'funding'),
    funding.entity_relations %>% select(entity = src_entity) %>% mutate(use = 'src_entity'),
    settlement.addr_entities %>% select(entity = settlement_entity) %>% mutate(use = 'settlement'),
    settlement.entity_relations %>% select(entity = dst_entity) %>% mutate(use = 'dst_entity')
  ) %>% 
    unique %>%
    mutate(seen = 1) %>%
    pivot_wider(names_from = use, values_from = seen) %>%
    left_join(
      bind_rows(
        funding.entity_stats,
        settlement.entity_stats
      ) %>% unique,
      by = 'entity'
    ) %>%
    left_join(address.categories, by = c('repr_address'= 'address'))
  
  entity_relations <<- bind_rows(
      funding.entity_relations %>%
        select(source = src_entity, target = funding_entity, no_transactions, value) %>%
        mutate(use = 'funding'),
      settlement.entity_relations %>%
        select(target = dst_entity, source = settlement_entity, no_transactions, value) %>%
        mutate(use = 'settlement')
    ) %>%
      mutate(use = as.factor(use))
}

load_dataset()

```


```{r export_all_entities, include=FALSE}

entities %>%
  select(entity, repr_address, funding, src_entity, settlement, dst_entity) %>%
  write.csv(file = paste0(dataset.path, "views/all_entities_w_repr_addresses.csv"), row.names = FALSE)

entities %>%
  select(address = repr_address) %>%
  write.csv(file = paste0(dataset.path, "views/repr_addresses.csv"), row.names = FALSE)

entity_relations %>%
  select(source, target, use) %>%
  inner_join(entities, by = c('source' = 'entity')) %>%
  select(source, source_repr_address = repr_address, target, use) %>%
  inner_join(entities, by = c('target' = 'entity')) %>%
  select(source, source_repr_address, target, target_repr_address = repr_address, use) %>%
  write.csv(file = paste0(dataset.path, "views/all_entity_relations_w_repr_addresses.csv"), row.names = FALSE)
```


## Dataset Overview

```{r summarize_datasets, echo=FALSE, message=FALSE, results='asis'}

tbl.dataset <- tibble(
  c("Source", "Funding", "Settlement", "Destination"),
  no_addresses = c(
    NA,
    addresses %>% filter(funding == 1) %>% nrow,
    addresses %>% filter(settlement == 1) %>% nrow,
    NA
  ),
  no_entities = c(
    entities %>% filter(src_entity == 1) %>% nrow,
    entities %>% filter(funding == 1) %>% nrow,
    entities %>% filter(settlement == 1) %>% nrow,
    entities %>% filter(dst_entity == 1) %>% nrow
  ),
  exp_addresses = c(
    entities %>% filter(src_entity == 1) %>% select(no_addresses) %>% sum,
    entities %>% filter(funding == 1) %>% select(no_addresses) %>% sum,
    entities %>% filter(settlement == 1) %>% select(no_addresses) %>% sum,
    entities %>% filter(dst_entity == 1) %>% select(no_addresses) %>% sum
  ),
  services = c(
    entities %>% filter(src_entity == 1 & !is.na(category)) %>% nrow,
    entities %>% filter(funding == 1 & !is.na(category)) %>% nrow,
    entities %>% filter(settlement == 1 & !is.na(category)) %>% nrow,
    entities %>% filter(dst_entity == 1 & !is.na(category)) %>% nrow
  ),
  relations = c(
    NA,
    entity_relations %>% filter(use == 'funding') %>% nrow,
    entity_relations %>% filter(use == 'settlement') %>% nrow,
    NA
  )
)

xt <- tbl.dataset %>%
  xtable(
    align = c("l", "@{\\extracolsep{\\fill}}l", rep("r", 5)),
    digits = c(0, 0, 0, 0, 0, 0, 0)
  )
names(xt) <- c("", "# Addresses", "# Entities", "# Addresses (Exp.)", "# Services", "# Relations")

print(xt,
      file = paste0(paper.path, "tables/dataset_overview.tex"),
      table.placement = "tbp",
      floating = FALSE,
      latex.environments = "center",
      include.rownames = FALSE,
      comment = TRUE,
      booktabs = TRUE,
      tabular.environment = "tabular*",
      width="\\textwidth",
      format.args = list(big.mark = ",", decimal.mark = ".")
)

print(xt,
      include.rownames = FALSE,
      comment = FALSE
)

```

## Services Overview

```{r service_stats, echo=FALSE, message=FALSE, fig.height=3, fig.width=5}

rel_category_tags <- function(entity_df, ps) {
  entity_df %>%
  select(entity, category) %>%
    group_by(category) %>%
      summarize(count = n()) %>%
  arrange(desc(count)) %>%
  mutate(percentage = count / entities %>% nrow) %>%
  mutate(position = ps) %>%
  select(position, category, percentage)
}

bind_rows(
  (entities %>%
    filter(!is.na(category)) %>%
    filter(src_entity == 1) %>%
    rel_category_tags('source')
  ),
  (entities %>%
    filter(!is.na(category)) %>%
    filter(funding == 1) %>%
    rel_category_tags('funding')
  ),
  (entities %>%
    filter(!is.na(category)) %>%
    filter(settlement == 1) %>%
    rel_category_tags('settlement')
  ),
  (entities %>%
    filter(!is.na(category)) %>%
    filter(dst_entity == 1) %>%
    rel_category_tags('destination')
  )
) %>%
  ggplot(aes(x=position, y=percentage)) +
    geom_bar(aes(fill=category), stat='identity') +
    labs(x="Entity type", y="Percentage", fill="Category") +
    scale_y_continuous(labels=percent) +
    theme_light()
    
# ggsave(file = paste0(paper.path, "figures/entity_categories.pdf"))

```


```{r compute_components, include=FALSE}

compute_components <- function(edges, nodes) {
  comp <- graph.data.frame(edges, nodes, directed = TRUE) %>% components
  data.frame(
    entity = as.numeric(names(comp$membership)),
    component = comp$membership,
    row.names = NULL
  )
}

entities <- entities %>%
  left_join(
    compute_components(
      entity_relations %>% filter(use == 'funding') %>% select(source, target),
      entities %>% filter(funding == 1 | src_entity == 1) %>% select(entity)
    ) %>% select(entity, funding_component = component),
    by = 'entity'
  ) %>%
  left_join(
    compute_components(
      entity_relations %>% filter(use == 'settlement') %>% select(source, target),
      entities %>% filter(settlement == 1 | dst_entity == 1) %>% select(entity)
    ) %>% select(entity, settlement_component = component),
    by = 'entity'
  )

components.funding <- entities %>%
  filter(!is.na(funding_component)) %>%
  group_by(funding_component, src_entity, funding) %>%
  summarize(
    size = n(),
  ) %>%
  mutate(type = case_when(
    !is.na(src_entity) & is.na(funding) ~ 'source',
    is.na(src_entity) & !is.na(funding) ~ 'funding',
    !is.na(src_entity) & !is.na(funding) ~ 'both',    
  )) %>%
  ungroup %>%
  select(component = funding_component, size, type) %>%
  pivot_wider(names_from = type, values_from = size) %>%
  rowwise %>%
    mutate(size = sum(both, source, funding, na.rm = TRUE)) %>%
  ungroup %>%
  replace(., is.na(.), 0)

components.settlement <- entities %>%
  filter(!is.na(settlement_component)) %>%
  group_by(settlement_component, settlement, dst_entity) %>%
  summarize(
    size = n(),
  ) %>%
  mutate(type = case_when(
    !is.na(settlement) & is.na(dst_entity) ~ 'settlement',
    is.na(settlement) & !is.na(dst_entity) ~ 'destination',
    !is.na(settlement) & !is.na(dst_entity) ~ 'both',    
  )) %>%
  ungroup %>%
  select(component = settlement_component, size, type) %>%
  pivot_wider(names_from = type, values_from = size) %>%
  rowwise %>%
    mutate(size = sum(both, destination, settlement, na.rm = TRUE)) %>%
  ungroup %>%
  replace(., is.na(.), 0)
```

# Exploring the Funding Egonets

## Funding Egonets | Component Size Distribution

```{r funding_network_components_stats, echo=FALSE, fig.height=3, fig.width=5, message=FALSE}

# Plot component size distribution
components.funding %>%
  group_by(size) %>%
    summarize(count = n()) %>%
  ggplot(aes(x=size, y=count)) +
  geom_point(shape=1) +
  scale_x_log10(breaks=c(2,10,100,1000,10000,50000,100000)) +
  labs(x = "Size", y = "Count")
```

## Funding Egonets | Observations

- Number of connected components: `r components.funding %>% nrow`

- Distribution is highly skewed: `r  components.funding %>% filter(size == 2) %>% nrow` components have just two nodes (one source entity, one funding entity); we can safely ignore them.

- We also ignore the tail (`r components.funding %>% filter(size > 1000) %>% nrow` components > 1000 entities)

- Remaining components: `r components.funding %>% filter(size > 2 & size <= 1000) %>% nrow`


```{r component_extraction_visualization, include=FALSE}

# Plots a network for a single component
plot_component <- function(component_id, side) {
  if(side == 'funding') {
    entities_filtered <- entities %>% filter(funding_component == component_id)
    relations_filtered <- entity_relations %>% filter(use == 'funding')
  } else if(side == 'settlement') {
    entities_filtered <- entities %>% filter(settlement_component == component_id)
    relations_filtered <- entity_relations %>% filter(use == 'settlement')
  }
  relations_filtered <- relations_filtered %>%
    filter(source %in% entities_filtered$entity & target %in% entities_filtered$entity) %>%
    select(source, target)
  component <- graph.data.frame(relations_filtered, entities_filtered, directed = TRUE)
  V(component)$size <- scales::rescale(V(component)$no_addresses, to=c(5,25))
  V(component)$size <- 10
  V(component)$label <- NA
  if(side == 'funding') {
    V(component)$color <- case_when(
      is.na(entities_filtered$funding) & !is.na(entities_filtered$src_entity) ~ 'red2',
      !is.na(entities_filtered$funding) & is.na(entities_filtered$src_entity) ~ 'green2',
      !is.na(entities_filtered$funding) & !is.na(entities_filtered$src_entity) ~ 'yellow2'
    )
  } else if(side == 'settlement') {
    V(component)$color <- case_when(
      is.na(entities_filtered$settlement) & !is.na(entities_filtered$dst_entity) ~ 'red2',
      !is.na(entities_filtered$settlement) & is.na(entities_filtered$dst_entity) ~ 'green2',
      !is.na(entities_filtered$settlement) & !is.na(entities_filtered$dst_entity) ~ 'yellow2'
    )
  }
  plot(component, layout = layout.fruchterman.reingold, vertex.label.dist=3)
}

```


## Funding Egonets | Star Pattern

* A set of funding entities (green) within a component receives funds from the same source entities. These funding entities can also be the source for other funding entities.

* **Funding entities of each component can be clustered**

* Component filtering condition: source == 1 & funding > 1 & both == 0

```{r annotate_star_pattern, echo=FALSE, include=FALSE}

components.funding.star <- components.funding %>%
  filter(source == 1 & funding > 1 & both == 0) %>%
  select(component) %>%
  mutate(pattern = "star")
  
```

## Funding Egonets | Star Pattern | Example

```{r plot_star_pattern_to_pdf, echo=FALSE, message=FALSE, eval = FALSE}

pdf(file=paste0(results.path, "star_pattern.pdf"))  

trash <- lapply(components.funding.star$component, plot_component, 'funding')

dev.off()
    
```



```{r plot_star_pattern, echo=FALSE, message=FALSE}

plot_component(4283, 'funding')
    
```

## Funding Egonets | Snake Pattern

* A single source entity (red) funds an entity that is used for funding and also funds another funding entity (yellow) - we call them *dual use* entity.

* **Funding and dual use entities can be clustered **

* Component filtering condition: source == 1 & funding >= 1 & both > 0

```{r annotate_snake_pattern, echo=FALSE, include=FALSE}

components.funding.snake <- components.funding %>%
  filter(source == 1 & funding >= 1 & both > 0) %>%
  select(component) %>%
  mutate(pattern = "snake")

```

## Funding Egonets | Snake Pattern | Example

```{r plot_snake_pattern_to_pdf, echo=FALSE, message=FALSE, eval = FALSE}

pdf(file=paste0(results.path, "snake_pattern.pdf"))  

trash <- lapply(components.funding.snake$component, plot_component, 'funding')

dev.off()
    
```

```{r plot_snake_pattern, echo=FALSE, message=FALSE}
plot_component(6, 'funding')
```

## Funding Egonets | All Patterns | Funding Entities

```{r funding_plot_funding_entities, echo=FALSE, fig.height=3, fig.width=5, message=FALSE}

entities %>%
  inner_join(
    bind_rows(components.funding.star, components.funding.snake),
    by = c('funding_component' = 'component')
  ) %>%
  select(entity, src_entity, funding, no_addresses, category, pattern) %>%
  filter(funding == 1) %>%
  ggplot(aes(x=pattern, y=no_addresses)) +
    geom_violin() +
    # geom_point(aes(color = category)) +
    geom_point() +
    scale_y_log10()

```


## Funding Egonets | All Patterns | Source Entities

```{r funding_plot_source_entities, echo=FALSE, fig.height=3, fig.width=5, message=FALSE}

entities %>%
  inner_join(
    bind_rows(components.funding.star, components.funding.snake),
    by = c('funding_component' = 'component')
  ) %>%
  select(entity, src_entity, funding, no_addresses, category, pattern) %>%
  filter(src_entity == 1) %>%
  ggplot(aes(x=pattern, y=no_addresses)) +
    geom_violin() +
    geom_point(aes(color = category)) +
    scale_y_log10()

```


## Funding Egonets | All Patterns | Observations

* Funding entities are generally non-service wallets; just one "hosted wallet" exception

* Many source entities in both patterns are service wallets, especially those with a high number of addresses

* Filtering strategy:
** Star pattern: filter out all components that involve a service entity
** Snake pattern: filter all components that involve a funding service entity

For both patterns we filter components that involve a service either on the source or funding side

```{r filter_funding_patterns, echo=FALSE, message=FALSE, results="asis"}

components.funding.star <- components.funding.star %>%
  left_join(
    entities %>%
      filter(!is.na(category)) %>%
      select(funding_component) %>%
      mutate(filtered = 1) %>%
      unique,
    by = c('component' = 'funding_component')
  )

components.funding.snake <- components.funding.snake %>%
  left_join(
    entities %>%
      filter(funding == 1) %>%
      filter(!is.na(category)) %>%
      select(funding_component) %>%
      mutate(filtered = 1) %>%
      unique,
    by = c('component' = 'funding_component')
  )

```

## Funding Egonets | Results

```{r funding.results, echo=FALSE, results="asis"}

data.frame(
  Rownames = c("Total (filtered)","Relevant (> 2)", "Star","Star (Filtered)", "Snake", "Snake (Filtered)"),
  Components = c(
    components.funding %>% nrow,
    components.funding %>% filter(size > 2) %>% nrow,
    components.funding.star %>% nrow,
    components.funding.star %>% filter(is.na(filtered)) %>% nrow,
    components.funding.snake %>% nrow,
    components.funding.snake %>% filter(is.na(filtered)) %>% nrow
  ),
  Clustered_Entities = c(
    entities %>% filter(!is.na(funding_component)) %>% nrow,
    entities %>%
      inner_join(components.funding, by = c('funding_component' = 'component')) %>% filter(size > 2) %>% nrow,
    entities %>%
      inner_join(components.funding.star, by = c('funding_component' = 'component')) %>% filter(!is.na(funding)) %>% nrow,
    entities %>%
      inner_join(components.funding.star %>% filter(is.na(filtered)), by = c('funding_component' = 'component'))  %>% filter(!is.na(funding)) %>% nrow,
    entities %>%
      inner_join(components.funding.snake, by = c('funding_component' = 'component')) %>% filter(!is.na(funding)) %>% nrow,
    entities %>%
      inner_join(components.funding.snake %>% filter(is.na(filtered)), by = c('funding_component' = 'component')) %>% filter(!is.na(funding)) %>% nrow
  )
) %>%
column_to_rownames(var = "Rownames") %>%
xtable %>%
  print(comment = FALSE, include.rownames = TRUE, format.args=list(big.mark = ",", decimal.mark = "."))

```

```{r export_funding_patterns, echo=FALSE, message=FALSE, results="asis"}

entities %>%
  inner_join(components.funding.star, by = c('funding_component' = 'component')) %>%
  filter(!is.na(funding)) %>%
  select(component = funding_component, entity) %>%
  arrange(component) %>%
  write.csv(file = paste0(results.path, "funding_cluster_star_pattern.csv"), row.names = FALSE)

entities %>%
  inner_join(components.funding.star, by = c('funding_component' = 'component')) %>%
  filter(!is.na(funding) & is.na(filtered)) %>%
  select(component = funding_component, entity) %>%
  arrange(component) %>%
  write.csv(file = paste0(results.path, "funding_cluster_star_pattern_filtered.csv"), row.names = FALSE)

entities %>%
  inner_join(components.funding.snake, by = c('funding_component' = 'component')) %>%
  filter(!is.na(funding)) %>%
  select(component = funding_component, entity) %>%
  arrange(component) %>%
  write.csv(file = paste0(results.path, "funding_cluster_snake_pattern.csv"), row.names = FALSE)

entities %>%
  inner_join(components.funding.snake, by = c('funding_component' = 'component')) %>%
  filter(!is.na(funding)& is.na(filtered)) %>%
  select(component = funding_component, entity) %>%
  arrange(component) %>%
  write.csv(file = paste0(results.path, "funding_cluster_snake_pattern_filtered.csv"), row.names = FALSE)

```


# Exploring the Settlement Egonets

## Settlement Egonets | Component Size Distribution

```{r settlement_network_components_stats, echo=FALSE, fig.height=3, fig.width=5, message=FALSE}

# Plot component size distribution
components.settlement %>%
  group_by(size) %>%
    summarize(count = n()) %>%
  ggplot(aes(x=size, y=count)) +
  geom_point(shape=1) +
  scale_x_log10(breaks=c(2,10,100,500, 1000)) +
  labs(x = "Size", y = "Count")
```

## Settlement Egonets | Observations

- Number of connected components: `r components.settlement %>% nrow` (incl. size 1)

- Distribution is highly skewed: `r  components.settlement %>% filter(size == 2) %>% nrow` components have just one or two nodes (one source entity, one funding entity); we can safely ignore them.

- The largest component has `r components.settlement$size %>% max` components. We include all of them in our analysis

- Remaining components: `r components.settlement %>% filter(size > 2 & size <= 1000) %>% nrow`

## Settlement Egonets | Collector Pattern

* Several settlement entities (green) forward / collect their funds to the same destination entities (red). The destination might also have received funds from entites, which is not reflected in our dataset.

* **Settlement entities of each collector pattern component can be clustered**

* Component filtering condition: settlement > 1 & destination == 1 & both == 0

```{r annotate_collector_pattern, echo=FALSE, include=FALSE}

components.settlement.collector <- components.settlement %>%
  filter(settlement > 1 & destination == 1 & both == 0) %>%
  select(component) %>%
  mutate(pattern = "collector")

```

## Settlement Egonets | Collector Pattern | Example

```{r plot_collector_pattern_to_pdf, echo=FALSE, message=FALSE, eval = FALSE}

pdf(file=paste0(results.path, "collector_pattern.pdf"))  

trash <- lapply(components.settlement.collector$component, plot_component, 'settlement')

dev.off()
    
```


```{r plot_collector_pattern, echo=FALSE, message=FALSE}
plot_component(56, 'settlement')
```

## Settlement Egonets | Collector Proxy Pattern

* Several settlement entities (green) forward / collect their funds in a proxy, which by itself seves as a settlement entity. That entity then forwards funds to a collector.

* Settlement entities can also forward funds to other settlement entities (collector proxies)

* **Settlement and proxy collector entities can be clustered**

* Component filtering condition: settlement >= 0 & destination >= 1 & both > 0

```{r annotate_collector_ext__pattern, echo=FALSE, include=FALSE}

components.settlement.collector_ext <- components.settlement %>%
  filter(settlement >= 0 & destination == 1 & both > 0) %>%
  select(component) %>%
  mutate(pattern = "collector_ext")

```

## Settlement Egonets | Collector Proxy Pattern | Example

```{r plot_proxy_pattern_to_pdf, echo=FALSE, message=FALSE, eval = FALSE}

pdf(file=paste0(results.path, "proxy_pattern.pdf"))  

trash <- lapply(components.settlement.collector_ext$component, plot_component, 'settlement')

dev.off()
    
```

```{r plot_collector_ext_pattern, echo=FALSE, message=FALSE}
plot_component(75, 'settlement')
```
## Settlement Egonets | All Patterns | Settlement Entities

```{r settlement_plot_funding_entities, echo=FALSE, fig.height=3, fig.width=5, message=FALSE}

entities %>%
  inner_join(
    bind_rows(components.settlement.collector, components.settlement.collector_ext),
    by = c('settlement_component' = 'component')
  ) %>%
  select(entity, dst_entity, settlement, no_addresses, category, pattern) %>%
  filter(settlement == 1) %>%
  ggplot(aes(x=pattern, y=no_addresses)) +
    geom_violin() +
    # geom_point(aes(color = category)) +
    geom_point() +
    scale_y_log10()

```
## Settlement Egonets | All Patterns | Destination Entities

```{r settlement_plot_destination_entities, echo=FALSE, fig.height=3, fig.width=5, message=FALSE}

entities %>%
  inner_join(
    bind_rows(components.settlement.collector, components.settlement.collector_ext),
    by = c('settlement_component' = 'component')
  ) %>%
  select(entity, dst_entity, settlement, no_addresses, category, pattern) %>%
  filter(dst_entity == 1) %>%
  ggplot(aes(x=pattern, y=no_addresses)) +
    geom_violin() +
    geom_point(aes(color = category)) +
    scale_y_log10()

```
## Funding Egonets | All Patterns | Observations

* Destination entities with high address cardinality are services

* Settlement entities have low address cardinality

* Strategy:
  
  * we filter all collector components that involve a service entity


```{r filter_settlement_patterns, echo=FALSE, message=FALSE, results="asis"}

components.settlement.collector <- components.settlement.collector %>%
  left_join(
    entities %>%
      filter(!is.na(category)) %>%
      select(settlement_component) %>%
      mutate(filtered = 1) %>%
      unique,
    by = c('component' = 'settlement_component')
  )

components.settlement.collector_ext <- components.settlement.collector_ext %>%
  left_join(
    entities %>%
      filter(!is.na(category)) %>%
      select(settlement_component) %>%
      mutate(filtered = 1) %>%
      unique,
    by = c('component' = 'settlement_component')
  )

```

```{r settlement.results.export, echo=FALSE, include=FALSE}

entities %>%
  inner_join(components.settlement.collector, by = c('settlement_component' = 'component')) %>%
  filter(!is.na(settlement)) %>%
  select(component = settlement_component, entity) %>%
  arrange(component) %>%
  write.csv(file = paste0(results.path, "settlement_cluster_collector_pattern.csv"), row.names = FALSE)

entities %>%
  inner_join(components.settlement.collector, by = c('settlement_component' = 'component')) %>%
  filter(!is.na(settlement) & is.na(filtered)) %>%
  select(component = settlement_component, entity) %>%
  arrange(component) %>%
  write.csv(file = paste0(results.path, "settlement_cluster_collector_pattern_filtered.csv"), row.names = FALSE)

entities %>%
  inner_join(components.settlement.collector_ext, by = c('settlement_component' = 'component')) %>%
  filter(!is.na(settlement)) %>%
  select(component = settlement_component, entity) %>%
  arrange(component) %>%
  write.csv(file = paste0(results.path, "settlement_cluster_collector_pattern_extended.csv"), row.names = FALSE)

entities %>%
  inner_join(components.settlement.collector_ext, by = c('settlement_component' = 'component')) %>%
  filter(!is.na(settlement) & is.na(filtered)) %>%
  select(component = settlement_component, entity) %>%
  arrange(component) %>%
  write.csv(file = paste0(results.path, "settlement_cluster_collector_pattern_extended_filtered.csv"), row.names = FALSE)
```

## Settlement Egonets | Results

```{r settlement.results, echo=FALSE, results="asis"}

data.frame(
  Rownames = c("Total", "Relevant (> 2)",
               "Collector", "Collector (filtered)", "Collector Ext.", "Collector Ext. (filtered)"),
  Components = c(
    components.settlement %>% nrow,
    components.settlement %>% filter(size > 2) %>% nrow,
    components.settlement.collector %>% nrow,
    components.settlement.collector %>% filter(is.na(filtered)) %>% nrow,
    components.settlement.collector_ext %>% nrow,
    components.settlement.collector_ext %>% filter(is.na(filtered)) %>% nrow
  ),
  Entities = c(
    entities %>% filter(!is.na(settlement_component)) %>% nrow,
    entities %>%
      inner_join(components.settlement, by = c('settlement_component' = 'component')) %>% filter(size > 2) %>% nrow,
    entities %>%
      inner_join(components.settlement.collector, by = c('settlement_component' = 'component')) %>% filter(!is.na(settlement)) %>% nrow,
    entities %>%
      inner_join(components.settlement.collector %>% filter(is.na(filtered)), by = c('settlement_component' = 'component')) %>% filter(!is.na(settlement)) %>% nrow,
    entities %>%
      inner_join(components.settlement.collector_ext, by = c('settlement_component' = 'component')) %>% filter(!is.na(settlement)) %>% nrow,
    entities %>%
      inner_join(components.settlement.collector_ext %>% filter(is.na(filtered)), by = c('settlement_component' = 'component')) %>% filter(!is.na(settlement)) %>% nrow  
  )
) %>%
column_to_rownames(var = "Rownames") %>%
xtable %>%
  print(comment = FALSE, include.rownames = TRUE, format.args=list(big.mark = ",", decimal.mark = "."))

```

# Results

## On-Chain Clustering

```{r overall.results, echo=FALSE, results="asis"}

no_components.star <- components.funding.star %>% filter(is.na(filtered)) %>% nrow

no_components.snake <- components.funding.snake %>% filter(is.na(filtered)) %>% nrow

no_components.collector <- components.settlement.collector %>% filter(is.na(filtered)) %>% nrow

no_components.proxy <- components.settlement.collector_ext %>% filter(is.na(filtered)) %>% nrow
  
no_entities.star <- entities %>%
  inner_join(
    components.funding.star %>% filter(is.na(filtered)),
    by = c('funding_component' = 'component')) %>% filter(!is.na(funding)) %>% nrow

no_entities.snake <- entities %>%
  inner_join(
    components.funding.snake %>% filter(is.na(filtered)),
    by = c('funding_component' = 'component')) %>% filter(!is.na(funding)) %>% nrow

no_entities.collector <- entities %>%
  inner_join(
    components.settlement.collector %>% filter(is.na(filtered)),
    by = c('settlement_component' = 'component')) %>% filter(!is.na(settlement)) %>% nrow

no_entities.proxy <- entities %>%
  inner_join(
    components.settlement.collector_ext %>% filter(is.na(filtered)),
    by = c('settlement_component' = 'component')) %>% filter(!is.na(settlement)) %>% nrow

no_addresses.star <- entities %>%
  inner_join(
    components.funding.star %>% filter(is.na(filtered)),
    by = c('funding_component' = 'component')) %>% filter(!is.na(funding)) %>%
  select(no_addresses) %>% sum

no_addresses.snake <- entities %>%
  inner_join(
    components.funding.snake %>% filter(is.na(filtered)),
    by = c('funding_component' = 'component')) %>% filter(!is.na(funding)) %>%
  select(no_addresses) %>% sum

no_addresses.collector <- entities %>%
  inner_join(
    components.settlement.collector %>% filter(is.na(filtered)),
    by = c('settlement_component' = 'component')) %>% filter(!is.na(settlement)) %>%
  select(no_addresses) %>% sum

no_addresses.proxy <- entities %>%
  inner_join(
    components.settlement.collector_ext %>% filter(is.na(filtered)),
    by = c('settlement_component' = 'component')) %>% filter(!is.na(settlement)) %>%
  select(no_addresses) %>% sum


tbl.results <- tibble(
  c("Star (F)", "Snake (F)", "Collector (S)", "Proxy (S)", "Total"),
  no_components = c(
    no_components.star,
    no_components.snake,
    no_components.collector,
    no_components.proxy,
    no_components.star + no_components.snake + no_components.collector + no_components.proxy
  ),
  no_components_rel = c(
    no_components.star / components.funding %>% filter(size > 2) %>% nrow,
    no_components.snake / components.funding %>% filter(size > 2) %>% nrow,
    no_components.collector / components.settlement %>% filter(size > 2) %>% nrow,
    no_components.proxy / components.settlement %>% filter(size > 2) %>% nrow,
    no_components.star / components.funding %>% filter(size > 2) %>% nrow +
      no_components.snake / components.funding %>% filter(size > 2) %>% nrow +
      no_components.collector / components.settlement %>% filter(size > 2) %>% nrow +
      no_components.proxy / components.settlement %>% filter(size > 2) %>% nrow
  ),
  no_entities = c(
    no_entities.star,
    no_entities.snake,
    no_entities.collector,
    no_entities.proxy,
    no_entities.star + no_entities.snake + no_entities.collector + no_entities.proxy
  ),
  no_entities_rel = c(
    no_entities.star / entities %>% filter(funding == 1) %>% nrow,
    no_entities.snake / entities %>% filter(funding == 1) %>% nrow,
    no_entities.collector / entities %>% filter(settlement == 1) %>% nrow,
    no_entities.proxy / entities %>% filter(settlement == 1) %>% nrow,
    no_entities.star / entities %>% filter(funding == 1) %>% nrow +
      no_entities.snake / entities %>% filter(funding == 1) %>% nrow +
      no_entities.collector / entities %>% filter(settlement == 1) %>% nrow +
      no_entities.proxy / entities %>% filter(settlement == 1) %>% nrow
  ),
  no_addresses = c(
    no_addresses.star,
    no_addresses.snake,
    no_addresses.collector,
    no_addresses.proxy,
    no_addresses.star + no_addresses.snake + no_addresses.collector + no_addresses.proxy
  ),
  no_addresses_rel = c(
    no_addresses.star / entities %>% filter(funding == 1) %>% select(no_addresses) %>% sum,
    no_addresses.snake / entities %>% filter(funding == 1) %>% select(no_addresses) %>% sum,
    no_addresses.collector / entities %>% filter(settlement == 1) %>% select(no_addresses) %>% sum,
    no_addresses.proxy / entities %>% filter(settlement == 1) %>% select(no_addresses) %>% sum,
    no_addresses.star / entities %>% filter(funding == 1) %>% select(no_addresses) %>% sum +
      no_addresses.snake / entities %>% filter(funding == 1) %>% select(no_addresses) %>% sum +
      no_addresses.collector / entities %>% filter(settlement == 1) %>% select(no_addresses) %>% sum +
      no_addresses.proxy / entities %>% filter(settlement == 1) %>% select(no_addresses) %>% sum
  )
)

xt <- tbl.results %>%
  xtable(
    align = c("l", "@{\\extracolsep{\\fill}}l", rep("r", 6)),
    digits = c(0, 2, 0, 2, 0, 2, 0, 2)
  )
names(xt) <- c("", "Abs", "Rel", "Abs", "Rel", "Abs", "Rel")

print(xt,
      file = paste0(paper.path, "tables/clustering_results_onchain.tex"),
      table.placement = "tbp",
      floating = FALSE,
      latex.environments = "center",
      include.rownames = FALSE,
      comment = TRUE,
      booktabs = TRUE,
      tabular.environment = "tabular*",
      width="\\textwidth",
      format.args = list(big.mark = ",", decimal.mark = "."),
      hline.after = c(0, 4, 5),
      add.to.row = list(pos = list(-1),
                        command=c(paste("\\toprule\n&\\multicolumn{2}{c}{\\# Components} &",
                                        "\\multicolumn{2}{c}{\\# Entities} &",
                                        "\\multicolumn{2}{c}{\\# Addresses}\\\\\n")))
)

print(xt,
      include.rownames = FALSE,
      comment = FALSE,
      hline.after = c(0, 4, 5),
      format.args = list(big.mark = ",", decimal.mark = ".")
)

```



```{r export_gephi_graphs, include=FALSE}

entities %>%
  inner_join(
    bind_rows(components.funding.snake, components.funding.star) %>%
      select(component),
    by = c('funding_component' = 'component')
  ) %>%
  mutate(type = case_when(
    funding == 1 & is.na(src_entity) ~ 'funding',
    is.na(funding) & src_entity == 1 ~ 'source',
    funding == 1 & src_entity == 1 ~ 'both'
  )) %>%
  select(id = entity, type, no_addresses) %>%
  write.csv(file = paste0(results.path, "gephi/funding_entity_nodes.csv"), row.names = FALSE)

entity_relations %>%
  filter(use == 'funding') %>%
  inner_join(
    entities %>%
      inner_join(
        bind_rows(components.funding.snake, components.funding.star) %>%
          select(component),
        by = c('funding_component' = 'component')),
    by = c('source' = 'entity')
  ) %>%
  inner_join(
    entities %>%
      inner_join(
        bind_rows(components.funding.snake, components.funding.star) %>%
          select(component),
        by = c('funding_component' = 'component')),
    by = c('target' = 'entity')
  ) %>%
  select(source, target, no_transactions, value) %>%
  write.csv(file = paste0(results.path, "gephi/funding_entity_edges.csv"), row.names = FALSE)

entities %>%
  inner_join(
    bind_rows(components.settlement.collector, components.settlement.collector_ext) %>%
      select(component),
    by = c('settlement_component' = 'component')
  ) %>%
  mutate(type = case_when(
    settlement == 1 & is.na(dst_entity) ~ 'settlement',
    is.na(settlement) & dst_entity == 1 ~ 'destination',
    settlement == 1 & dst_entity == 1 ~ 'both'
  )) %>%
  select(id = entity, type, no_addresses) %>%
  write.csv(file = paste0(results.path, "gephi/settlement_entity_nodes.csv"), row.names = FALSE)

entity_relations %>%
  filter(use == 'settlement') %>%
  inner_join(
    entities %>%
      inner_join(
        bind_rows(components.settlement.collector, components.settlement.collector_ext) %>%
          select(component),
        by = c('settlement_component' = 'component')),
    by = c('source' = 'entity')
  ) %>%
  inner_join(
    entities %>%
      inner_join(
        bind_rows(components.settlement.collector, components.settlement.collector_ext) %>%
          select(component),
        by = c('settlement_component' = 'component')),
    by = c('target' = 'entity')
  ) %>%
  select(source, target, no_transactions, value) %>%
  write.csv(file = paste0(results.path, "gephi/settlement_entity_edges.csv"), row.names = FALSE)

```
